Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2018-07-11 AnalyticStructure_main.tex
Update on Overleaf.

The molecule is oriented in the $xy$ plain and the $x$-dimension of the box is equal to 15.0, 18.2 and 19.7 \AA.
220 states have been computed in each setup and the corresponding
energy reange for the unoccupied statescutoff in the three simulation box is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).

>>>>

The molecule is oriented in the $xy$ plain and the $x$-dimension of the box is equal to 15.0, 18.2 and 19.7 \AA.
220 states have been computed in each setup and the corresponding
energy reange for the unoccupied states is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
